```{r message=FALSE}
source("util.R")
knitr::opts_chunk$set(fig.height=3, warning=FALSE)
source("data.R")
q <- quote(State=='Florida' & County=='Monroe')
#monroe <- zoo.nyt(eval(q))
monroe <- subset(zoo.jhu.US(eval(q)), confirmed > 0)
pop <- get.pop.US(eval(q))
```


### Q1: Is an outbreak starting?

Daily change in new cases (averaged over week):<br>
```{r}
autoplot(ave.daily.change(monroe$confirmed)) +
  geom_point() +
  geom_hline(yintercept = 0, linetype="dashed", color="grey") +
  theme(panel.grid.minor = element_blank()) +
  scale_x_eow(monroe$confirmed) +
  scale_y_daily_change()
```


### Q2: How dangerous is it now?

The following numbers evaluate "danger #2" in
<a href="../risk/two-dangers.html">this split of covid danger</a>.

For context, about <b>one death per week</b> is the rate of 
pneumonia/flu deaths in the Keys (based on Florida rates).

Covid deaths
<sup>
[ * ](https://ourworldindata.org/coronavirus#deaths-from-covid-19-background)
</sup>
per week:<br>
```{r}
autoplot.weekly.bar(weekly.deltas(monroe$deaths)) +
  scale_y_continuous(breaks=0:max(monroe$deaths))
```

See [a historical perspective](../risk/history.html) for a broad context.

<small>
[ * What is counted as a death from COVID-19?](https://ourworldindata.org/coronavirus#deaths-from-covid-19-background)
</small>

### Q3: Can the Keys "beat" coronavirus?

Weekly covid deaths
<sup>
[ * ](https://ourworldindata.org/coronavirus#deaths-from-covid-19-background)
</sup>
per million of "winning" counties<br>
compared with<br>
2% and 1% of Keys cases per million:<br>
```{r message=FALSE, fig.height=6}
asof <- end(monroe)
weekly.deaths <- function(country) {
  weekly.deltas(window(zoo.jhu.global.micro(country),end=asof))$deaths
}
taiwan <- weekly.deltas(window(zoo.jhu.global(Country=='Taiwan*'),end=asof)/23.8)
monroe.micro <- weekly.deltas(monroe$confirmed/pop*1e6)
winners <- window(merge(
  `2% Keys cases`= 0.02*monroe.micro,
  `1% Keys cases`= 0.01*monroe.micro,
  `Trinidad&Tobago`=weekly.deaths('Trinidad and Tobago'),
  `New Zealand`=weekly.deaths('New Zealand'),
  `Australia`=weekly.deaths('Australia'),
  Singapore=weekly.deaths('Singapore'),
  Japan=weekly.deaths('Japan'),
  Korea=weekly.deaths('Korea, South'),
  `Taiwan`=taiwan$deaths
), start="2020-03-01")
autoplot(winners, facet=NULL) +
  geom_point() +
  scale_x_eow(winners) +
  xlab("2020") +
  ylab("Weekly COVID Deaths Per Million")
```

### Further Details

New cases per week:<br>
```{r}
autoplot.weekly.bar(weekly.deltas(monroe$confirmed))
```

New cases per day:<br>
```{r}
autoplot(daily.deltas(monroe$confirmed), geom='blank') +
  scale_x_eow(monroe$confirmed) +
  geom_col()
```


#### Data check

County population = `r format(pop, big.mark=',')`

```{r results='asis'}
kable(tail(as.data.frame(monroe),3))
```

