
```{r}
source('retrogression.R')

retroyear <- function(mcmorts) {
  ifelse(mcmorts < pivot.mcmorts,
         log(mcmorts/ref.mcmort)/log.slope,
         2020 - pivot.year + (mcmorts-pivot.mcmorts)/linear.slope)
}

source("util.R")
source("data.R")
# knitr::opts_chunk$set(fig.height=12) 
```

```{r warning=FALSE, message=FALSE}
#us <- weekly.deltas(zoo.jhu.global.micro('US'))
wa.usa <- weekly.deltas(zoo.jhu.US.micro(State=='Washington'))
ma.usa <- weekly.deltas(zoo.jhu.US.micro(State=='Massachusetts'))
ca.usa <- weekly.deltas(zoo.jhu.US.micro(State=='California'))
#ny.usa <- weekly.deltas(zoo.nyt.micro(State=='New York'))
asof <- end(ma.usa)
ny.usa <- weekly.deltas(window(zoo.jhu.US.micro(State=='New York'),end=asof))
#sfc <- weekly.deltas(zoo.nyt.micro(State=='California' & County=='San Francisco'))
belgium <- weekly.deltas(window(zoo.jhu.global.micro('Belgium'),end=asof))
italy <- weekly.deltas(window(zoo.jhu.global.micro('Italy'),end=asof))
spain <- weekly.deltas(window(zoo.jhu.global.micro('Spain'),end=asof))
korea <- weekly.deltas(window(zoo.jhu.global.micro('Korea, South'),end=asof))
japan <- weekly.deltas(window(zoo.jhu.global.micro('Japan'),end=asof))
iran <- weekly.deltas(window(zoo.jhu.global.micro('Iran'),end=asof))
#indonesia <- weekly.deltas(zoo.jhu.global.micro('Indonesia'))
#singapore <- weekly.deltas(zoo.jhu.global.micro('Singapore'))
#china  <- weekly.deltas(zoo.jhu.global.micro('China'))
examples.2020 <- merge(
#  US=us$deaths,
  `MA, USA`=ma.usa$deaths,
  `NY, USA`=ny.usa$deaths,
  `WA, USA`=wa.usa$deaths,
  `CA, USA`=ca.usa$deaths,
#  `San Francisco`=sfc$deaths,
  Belgium=belgium$deaths,
  Italy=italy$deaths,
  Spain=spain$deaths,
  Iran=iran$deaths,
  Japan=japan$deaths,
  Korea=korea$deaths
#  Singapore=singapore$deaths,
#  China=china$deaths
) + ref.mcmort/52
```

As an alternative to looking at
[number of deaths per week](history.html)
a [mathematical formula](retrogression-math.html)
can convert weekly deaths per million into a more intuitive
measure of:

> *How many decades before 2020 must your retrogress to be living
> hypothetically with similar risk of Pathogenic Pulmonary Disease?*

The previous plots are redrawn below to this new scale of decades
of risk retrogression.


#### Decades (pre-2020) of risk retrogression, US historical (age-adjusted) vs 2020

```{r warning=FALSE}
top <- 20
Historical <- z.mcmorts/52
Historical[I(1918)] <- NA
Trend <- zoo((160:0)/10, as.numeric(1860:2020))
autoplot(merge(Trend, Historical=retroyear(Historical*52)/10),facet=NULL) +
  scale_x_continuous(breaks=seq(1860,2020,by=20)) +
  xlab("Year (1918 excluded)") +
  ylab("Decades of Retrogression") +
  scale_y_continuous(limits=c(0,top), breaks=seq(0,top, by=2))
autoplot(retroyear(examples.2020*52)/10,facet=NULL) +
  scale_y_continuous(limits=c(0,top), breaks=seq(0,top,by=2)) +
  xlab("2020") +
  ylab("Decades of Retrogression") +
  geom_point()
```

