
**As of `r format(max(jhu.data$Date), "%a %b %d")`**


## Plots Across Space

<div class="plot-title">(Average) Weekly Cases Per Million (over `r wnum` weeks)</div>
```{r warning=FALSE, fig.width=9, fig.height=4}
plot.trip(microcases %>% dzoo(weekly.deltas,wnum) %>% dzoo(tail,wnum)) +
  geom_path() +
  scale_y_continuous(limits=c(0,1600)) +
  labs(y="Weekly Cases Per Million")
```

<div class="plot-title">(Average) Weekly Deaths Per Million (over `r wnum` weeks)</div>
```{r warning=FALSE, fig.width=9, fig.height=4}
plot.trip(microdeaths %>% dzoo(weekly.deltas,wnum) %>% dzoo(tail,wnum)) +
  geom_path() +
  geom_hline(aes(yintercept=y, color=txt), hist.ref) +
  labs(y="Weekly Deaths Per Million")
```

<small>
 * 
"Average" means average during
the **entire "normal"** reference period of year(s),
not specifically during any epidemic.
</small>


## Plots Across Time

<div class="plot-title">(Average) Weekly Cases Per Million (every `r wnum` weeks)</div>
```{r warning=FALSE, fig.height=5}
df <- microcases %>% dzoo(weekly.deltas,wnum) %>% dzoo(window,start="2020-03-01")
plot.ts(df) +
  geom_path() +
  scale_y_continuous(limits=c(0,3000)) +
  labs(x="Date", y="Weekly Cases Per Million")
```

<div class="plot-title">(Average) Weekly Deaths Per Million (every `r wnum` weeks)</div>
```{r warning=FALSE, fig.height=5}
df <- microdeaths %>% dzoo(weekly.deltas,wnum) %>% dzoo(window,start="2020-03-01")
plot.ts(df) +
  geom_path() +
  scale_y_continuous(limits=c(0,250)) +
  geom_hline(aes(yintercept=y, linetype=txt), hist.ref) +
  labs(linetype=hist.txt) +
  labs(x="Date", y="Weekly Deaths Per Million")
```


## Data Details

<div class="table-title">Population</div>
```{r}
kable(trip.pop, format.args=list(big.mark=','))
```

<div class="table-title">Counties</div>
```{r}
kable(format.args=list(big.mark=','),
  trip %>% inner_join(US.POP) %>%
    mutate(FIPS=format(FIPS)) %>%
    select(Leg, State, County, FIPS, Population)
)
```

